Clustering time series based on probability distributions across temporal granularities

### 2021-11-08 main.Rmd
add tsne and sindex plot

```{r opt-cluster-tsne-jsd, fig.cap = "(a) shows t-SNE summary of the 24 customers chosen through prototype selection, (b) shows a plot of sindex for different cluster size $k$"}

>>>>

```{r opt-cluster-tsne-jsd, fig.cap = "(a) shows t-SNE summary of the $24$ selected customers chosen through prototype selection, (b) shows a plot of sindex for different cluster size."}
